### 2024-01-13 documentation/thesis/thesis_document.tex
more thesis

@@

@@

The present work aims to provide an efficient and comprehensive solution
for the design of low-field MRI devices by developing and implementing a
software and hardware framework.

@@

\hypertarget{state-of-the-art}{%
\chapter{State of the Art}\label{state-of-the-art}}

\hypertarget{conceptual-design}{%
\section{Conceptual Design}\label{conceptual-design}}

\begin{itemize}
\tightlist
\item
  etnwicklung eines hardware uns software framework zur einfachen
  aquirierung von Meagnetfelddaten
\item
  analysetools und funktionen
\end{itemize}

>>>>

Low-field magnetic resonance imaging (low-field \gls{mri}) is a
\gls{mri} technique that operates at a lower magnetic field strength
compared to conventional high-field \gls{mri} scanners. Typically, the
magnetic field in low-field MRI systems between
\passthrough{\lstinline!0.1T!} and \passthrough{\lstinline!0.3T!}
compared to the usual \passthrough{\lstinline!1.5T!} to
\passthrough{\lstinline!3T!} in high-field \gls{mri}
scanners.\cite{Hori2021-pt}

This technology is used in medical imaging as well as in preclinical
research. The main advantage of low-field MRI is the improved imaging of
soft tissues, especially when examining joints and muscles. It also
offers more cost-effective alternatives to high-field MRI
systems.\cite{Hori2021-pt}

\hypertarget{magnet-system}{%
\subsection{Magnet System}\label{magnet-system}}

@@

\hypertarget{state-of-the-art}{%
\section{State of the Art}\label{state-of-the-art}}

@@

The present work aims to provide an efficient and comprehensive solution
for the design of low-field \gls{mri} devices by developing and
implementing a software and hardware framework.

@@
